Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-10-30 manuscript.tex
20161030

\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. The tethered satellite system is modelled based on Lagrangian mechanics theory, and to overcome the limited input of the dynamic model, a new scalable dimensionless transform and strictly bounded terms are designed to guarantee the existence of the ratio between limited input and command signal. The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain, and the stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation to guarantee that the asymptotically stability of the deployment dynamics. The numerical simulations are reported to verify the effectiveness of the proposed control laws.
\end{abstract}
\begin{keyword}
Tethered satellite;  Sliding mode control;  Input limitation; Adaptive control
\end{keyword}
\end{frontmatter}
\section{Introduction}
The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique supports various applications for space exploration and scientific research, such as space debris removal~\cite{zhao2014thrust}, space elevator~\cite{kojima2015mission}, satellite de-orbit~\cite{zhong2013dynamics,zhong2013long} and the tethered space robot~\cite{huang2014optimal}. Many international space research institutes have launched some orbital, suborbital and ground experiments in an effort, such as TSS-1R, SEDS, MAST and YES2, to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results make researchers proceed to advance mechanics, kinetic and control studies intensively, to tackle the challenges of requirements from space missions in the future~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line}.\par

Recent scientific researches on deployment of the tethered satellite focus on the stabilization of the dynamics, and have varying merit and outcomes, providing different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approach~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}. Among the deployment stabilization strategies, the hybrid tension and thruster control boosts to the new developments. Iki et al. implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and the thruster was used to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}. Aslanov et al. presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system is excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}. Huang et al. investigated the attitude and deploying dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. Liu et al. equipped the thruster system, which consisted of four pairs of thrusters, in the subsatellite dedicating for regulation of the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages, the first stage of which ejected the tether with thruster to position the tether at desired beginning point of the second stage, and the second stage continued to adjust the tether to the stable vertical configuration by using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thrust-aided librating deployment of tape tethers, and the force acting on the tape tether included the tension and thruster force~\cite{mantellato2015thrust}. This hybrid strategy has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, thus is broadly utilized in reality compared with other control strategies.\par

@@

Based on the assumption above, the kinetic energy and the potential energy of the deployment dynamics can be described as~\cite{Mantellato2015}:

@@

T_t
&= \frac{1}{2}\sum\limits_{s=1}^2 m_s\bm{R_s'\cdot R_s'}\notag\\
&= \frac{1}{2}m\bm{R_0'\cdot R_0'}+\frac{1}{2}\sum\limits_{s=1}^2 m_s\bm{r_s'\cdot r_s'}\notag\\
&= \frac{1}{2}m\Omega^2R_0^2+\frac{1}{2}\bar{m}l^2\begin{bmatrix}\phi'+(\theta'+\Omega)^2\end{bmatrix}+\frac{1}{2}\bar{m}l'^2\label{eq:Tt1}\\
V_g
&= -\mu_e\sum\limits_{s=1}^2\frac{m_s}{\vert \bm{R_0+r_s}\vert}\notag\\
&= -m\Omega^2R_0^2+\frac{\bar{m}\Omega^2l^2}{2}(1-3\cos{^2\theta}\cos^2\phi),\label{eq:Vg}
where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively. $(\cdot)'$ represents the differentiation with respective to time, and $l$ means the tether length connecting the satellites. $\theta$ and $\phi$ depict the rolling and pitching dynamics of the TSS. For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
Combining Eq.~(\ref{eq:Vg}) and Eq.~(\ref{eq:Tt1}) give rise to the Lagrange function~\cite{Mantellato2015}:
L=&T_t-V_g\\
=&\frac{\bar ml^2}{2}\begin{pmatrix}\phi'^{2}+\cos^2\phi(\theta'+\Omega)^2\end{pmatrix}+\frac{\bar ml'^2}{2}\\
&-\frac{\bar m\Omega^2l^2}{2}\begin{pmatrix}1-3\cos^2\theta\cos^2\phi\end{pmatrix}+\frac{3m\Omega^2R_0^2}{2},
and utilize Lagrangian mechanics theory to obtain the following expression\cite{Sun2014304,Mantellato2015}

@@

\textcolor{red}{where $\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster and the out-of-plane thruster, respectively, and $\tau_t d$, $\tau_\theta d$ and $\tau_\phi d$ stand for the bounded external disturbances. Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:

@@

where $Y_r = Y_r(\bm q,\dot{\bm q},\dot{\bm q}_r,\ddot{\bm q}_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $S_r$ is able to be obtained, as follows:

@@

H(\bm q)\dot S_r+C(\bm q,\dot{\bm q})S_r=\bm\tau +\bm\tau_d- Y_r\Theta\label{eq:dynamic model 2}

@@

where $S_r$ is defined as

@@

S_r=\dot {\bm q}-\dot {\bm q}_r.\label{eq:Sr1}

@@

\dot{\bm\sigma}&=\bm{sign}(S)\\
S&=\Delta\dot{\bm q}+\alpha\Delta\bm q\label{eq:pid controller}

@@

and it's notable that the function above is saturated or bounded and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$. The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-\Delta h,\Delta h]$, and once the function $y=Sine(x)+\Delta h$ settles, one can chose the function $y = x+arcsin(\Delta h)$ such that

@@

@@

S_{r1} &= S_{q1}+\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\\
S_{q1} &= \bm{Sine}(\Delta \dot {\bm q}+\alpha\Delta\bm q),

@@

\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1e^{-2K_1^{-1}F^{-1}(t)}\bm{sign}(S_{r2})

@@

Consider dynamic coordinates change $S_{r2}$ with the regular error variable but not the $Sine$ form:

@@

S_{r2} &= S_{q2}+arcsin(\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma)\\
S_{q2} &= \Delta \dot {\bm q}+\alpha \Delta \bm q,

@@

It is obvious that $S_{q_1}$ is bounded, or exactly saturated, hence $S_{r_1}$ is also bounded if the dynamics can be controlled as desired. \textcolor{red}{In addition, for guaranteeing that $x=\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma$ always falls in the field of definition of $y=arcsin(x)$, $\gamma$ can be designed as a time-varying parameter

@@

    \gamma_0&\Vert\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert\le 1\\
    \gamma_0\left[\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\right]^{-1}&\Vert\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert> 1,

@@

    where $\gamma_0$ can be selected as $\gamma_0=0.1$, such that $\gamma\int_{t_0}^tS_{q1}d\varsigma$ is guaranteed to satisfy $\gamma\int_{t_0}^tS_{q1}d\varsigma\in[-1,1]$.}\par
According to Lemma~\ref{lemma:1}, it is apparent that $S_{r2}$ and $S_{r1}$ have the subsequent relation:

@@

&S_{r2}^T \bm{sign}(S_{r2}) \ge  S_{r1}^T \bm{sign}(S_{r1})\\
&\bm{sign}(S_{r2})=\bm{sign}(S_{r1}),

@@

Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinates change $S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $S_{r2}$ holds results in the following expression:

@@

H(q)\dot S_{r2} = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.

@@

V=\frac{1}{2}S_{r2}^TH(q)S_{r2}+\frac{1}{2}v^2,

@@

\dot V &= S_{r2}^TH(q)\dot S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}+v\dot v\\
&= -S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
&= -S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
&= -S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+v\dot v\\
&= -S_{r2}^TR_M(\delta\varphi F(t) \bm{sign}(S_{r1}))\delta\varphi F(t) \bm{sign}(S_{r1})+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}

@@

Since the command $ -\delta\varphi F(t) S_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ such that $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain a diagonal matrix as follows:

@@

v\dot v =\varphi\delta S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(S_{r2}),

@@

utilizing $\bm{sign}(S_{r1})=\bm{sign}(S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:

@@

\dot V&\le -S_{r2}^T\delta\varphi  K_1F(t)\bm{sign}(S_{r2})+S_{r2}^T(\varphi_1+\varphi_2) \bm{sign}(S_{r2})+\varphi\delta S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(S_{r2})\\
&\le \varphi S_{r2}^T\bm{sign}(S_{r2})-\varphi\delta S_{r2}^T \bm{sign}(S_{r2})\\
&\le\varphi(1-\delta)S_{r2}^T\bm{sign}(S_{r2})\le 0

@@

where a large enough $\delta>1$ can be selected such that $\dot V \le 0$. According to the description of Barbalat¡¯s lemmas, it implies that $S_{r2}$ asymptotically converges to origin. Also, the finite convergent time of desired sliding surface can be calculated by referring to~\cite{Ma201667}.}\par
\textcolor{red}{Utilizing $S_{r2}=0$ leads to the equation

@@

S_{q2}=-arcsin(\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma),\label{eq:eqSq2}

@@

and for employing Lyapunov second method to analyse the stabilities of $S_{q2}$ and $\Delta\bm q$, we firstly select a Lyapunov function candidate

@@

V_1 = \frac{1}{2}S_{q2}^TS_{q_2},

@@

\dot V_1 &= S_{q2}^T\dot S_{q_2}\\
&=-\frac{\gamma S_{q2}^TS_{q1}}{\sqrt{1-\Vert\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert^2}}\\
&\le -\frac{\gamma \Vert S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert^2}}\le 0,

@@

if and only if $S_{q1} = 0$, accordingly, $S_{q2} = 0$, one has $\dot V_1=0$. Hence the asymptotically stability of Eq.~(\ref{eq:eqSq2}) has been proved, and therefore $S_{q2}\rightarrow 0$ as $t\rightarrow \infty$ induces

@@

\dot Z = \vert Z\vert^{\hat\alpha} \bm{sign}(Z),

@@

\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r3}))

@@

S_{r3} &= S_{q3}+\gamma\int^t_{t_0}\Vert S_{q3}(\varsigma)\Vert^{\hat\alpha}  \bm{sign}(S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
S_{q3} &= \Delta \dot q+\alpha \bm{Sine}(\xi\Delta q),\label{eq:Sq3}

@@

where $0<\hat\alpha< 1$, such that the dynamics~(\ref{eq:dynamic model 2}) can be regulated as desired. $\varphi$ is the boundedness of the lumped uncertainty, and can be obtained by referring to Theorem~\ref{thm:1}.

@@

If the designer parameter $\hat\alpha = 1$, the quasi-saturated terminal sliding mode control degenerates into the quasi-saturated sliding mode control. Compared with the saturated sliding mode control, $S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method. This is because the establishment of the equation $\dot S_{q3} = \gamma\Vert S_{q3}\Vert^{\hat\alpha} \bm{ sign}(S_{q3})$.

@@

\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r4})),

@@

S_{r4} &= S_{q4}+\gamma\int^t_{t_0}S_{q4}(\varsigma) d\varsigma\\
S_{q4} &= \bm{Sine}(\Delta \dot q+\alpha\xi\Vert\Delta q\Vert^{\hat\alpha}\bm{sign}(\Delta q)),\label{eq:Sr4}

>>>>

\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. To overcome the limited input of the dynamic model, a new scalable dimensionless transform and strictly bounded terms are designed to guarantee the existence of the ratio between limited input and command signal. The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain, and the stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation to guarantee that the asymptotically stability of the deployment dynamics. The numerical simulations are reported to verify the effectiveness of the proposed control laws.
\end{abstract}
\begin{keyword}
Tethered satellite;  Sliding mode control;  Input limitation; Adaptive control
\end{keyword}
\end{frontmatter}
\section{Introduction}
The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique supports various applications for space exploration and scientific research, such as space debris removal, space elevator, satellite de-orbit and the tethered space robot~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}. Many international space research institutes have launched some orbital, suborbital and ground experiments in an effort, such as TSS-1R, SEDS, MAST and YES2, to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results make researchers proceed to advance mechanics, kinetic and control studies intensively, to tackle the challenges of requirements from space missions in the future~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.\par

Recent scientific researches on deployment of the tethered satellite focus on the stabilization of the dynamics, and have varying merit and outcomes, providing different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approach~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}. Among the deployment stabilization strategies, the hybrid tension and thruster control boosts to the new developments. Iki et al. implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and the thruster was used to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}. \textcolor{red}{Aslanov et al. presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system is excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}.} Huang et al. investigated the attitude and deploying dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. Liu et al. equipped the thruster system, which consisted of four pairs of thrusters, in the subsatellite dedicating for regulation of the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages, the first stage of which ejected the tether with thruster to position the tether at desired beginning point of the second stage, and the second stage continued to adjust the tether to the stable vertical configuration by using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thrust-aided librating deployment of tape tethers, and the force acting on the tape tether included the tension and thruster force~\cite{mantellato2015thrust}. This hybrid strategy has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, thus is broadly utilized in reality compared with other control strategies.\par

@@

%Based on the assumption above, the kinetic energy and the potential energy of the deployment dynamics can be described as~\cite{Mantellato2015}:

@@

%\begin{align}
%T_t
%&= \frac{1}{2}\sum\limits_{s=1}^2 m_s\bm{R_s'\cdot R_s'}\notag\\
%&= \frac{1}{2}m\bm{R_0'\cdot R_0'}+\frac{1}{2}\sum\limits_{s=1}^2 m_s\bm{r_s'\cdot r_s'}\notag\\
%&= \frac{1}{2}m\Omega^2R_0^2+\frac{1}{2}\bar{m}l^2\begin{bmatrix}\phi'+(\theta'+\Omega)^2\end{bmatrix}+\frac{1}{2}\bar{m}l'^2\label{eq:Tt1}\\
%V_g
%&= -\mu_e\sum\limits_{s=1}^2\frac{m_s}{\vert \bm{R_0+r_s}\vert}\notag\\
%&= -m\Omega^2R_0^2+\frac{\bar{m}\Omega^2l^2}{2}(1-3\cos{^2\theta}\cos^2\phi),\label{eq:Vg}
%\end{align}
%where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively. $(\cdot)'$ represents the differentiation with respective to time, and $l$ means the tether length connecting the satellites. $\theta$ and $\phi$ depict the rolling and pitching dynamics of the TSS. For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
%Combining Eq.~(\ref{eq:Vg}) and Eq.~(\ref{eq:Tt1}) give rise to the Lagrange function~\cite{Mantellato2015}:
%\begin{align}
%\begin{split}
%L=&T_t-V_g\\
%=&\frac{\bar ml^2}{2}\begin{pmatrix}\phi'^{2}+\cos^2\phi(\theta'+\Omega)^2\end{pmatrix}+\frac{\bar ml'^2}{2}\\
%&-\frac{\bar m\Omega^2l^2}{2}\begin{pmatrix}1-3\cos^2\theta\cos^2\phi\end{pmatrix}+\frac{3m\Omega^2R_0^2}{2},
%\end{split}
%\end{align}
Based on the assumption above and Lagrangian mechanics theory, we can directly obtain the following expression for the tethered satellite system~\cite{Sun2014304,Mantellato2015}

@@

\textcolor{red}{where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively. $(\cdot)'$ represents the differentiation with respective to time, and $l$ means the tether length connecting the satellites. $\theta$ and $\phi$ depict the rolling and pitching dynamics of the TSS. For clarity, $m_1m_2/m$ is rewritten as $\bar m$. $\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster and the out-of-plane thruster, respectively, and $\tau_t d$, $\tau_\theta d$ and $\tau_\phi d$ stand for the bounded external disturbances. Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:

@@

where $Y_r = Y_r(\bm q,\dot{\bm q},\dot{\bm q}_r,\ddot{\bm q}_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $\bm S_r$ is able to be obtained, as follows:

@@

H(\bm q)\dot {\bm S}_r+C(\bm q,\dot{\bm q})\bm S_r=\bm\tau +\bm\tau_d- Y_r\Theta\label{eq:dynamic model 2}

@@

where $\bm S_r$ is defined as

@@

\bm S_r=\dot {\bm q}-\dot {\bm q}_r.\label{eq:Sr1}

@@

\dot{\bm\sigma}&=\bm{sign}(\bm S)\\
\bm S&=\Delta\dot{\bm q}+\alpha\Delta\bm q\label{eq:pid controller}

@@

and it's notable that the function above is saturated and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$. The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-\Delta h,\Delta h]$, and once the function $y=Sine(x)+\Delta h$ settles, one can chose the function $y = x+arcsin(\Delta h)$ such that

@@

\begin{myrem}\textcolor{red}{Moreover, we think that a quantity $y$ or vector $\bm y$ is saturated iff it is produced directly by the saturated function $y=Sine(x)$ or $\bm y=\bm{Sine(x)}$. Otherwise, the bounded quantity is different from the saturated one since it does not own the standard formulation like $y=Sine(x)$, i.e., a quantity can just be said a bounded quantity if its boundary is $[a,b]$ with $a\neq -1$ or $b\neq 1$.}

@@

\bm S_{r1} &= \bm S_{q1}+\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\\
\bm S_{q1} &= \bm{Sine}(\Delta \dot {\bm q}+\alpha\Delta\bm q),

@@

\frac{d}{dt}F(t) = \delta\varphi \bm S_{r2}^T K_1e^{-2K_1^{-1}F^{-1}(t)}\bm{sign}(\bm S_{r2})

@@

Consider dynamic coordinates change $\bm S_{r2}$ with the regular error variable but not the $Sine$ form:

@@

\bm S_{r2} &= \bm S_{q2}+\bm{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma)\\
\bm S_{q2} &= \Delta \dot {\bm q}+\alpha \Delta \bm q,

@@

where $\bm y=\bm{arcsin}(\bm x)$ is the vector function with
\bm{arcsin}(\bm x) = \left(arcsin(x_1),arcsin(x_2),\cdots,arcsin(x_n)\right)^T
for a vector $\bm x=\left(x_1,x_2,\cdot,x_n\right)^T$. It is obvious that $\bm S_{q_1}$ is bounded, or exactly saturated, hence $\bm S_{r_1}$ is also bounded if the dynamics can be controlled as desired. \textcolor{red}{In addition, for guaranteeing that $\bm x=\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma$ always falls in the field of definition of $\bm y=arcsin(\bm x)$, $\gamma$ can be designed as a time-varying parameter

@@

    \gamma_0&\Vert\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert\le 1\\
    \gamma_0\Vert\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert^{-1}&\Vert\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert> 1,

@@

    where $\gamma_0$ can be selected as $\gamma_0=0.1$, such that $\gamma\int_{t_0}^t\bm S_{q1}d\varsigma$ is guaranteed to satisfy $\gamma\int_{t_0}^t\bm S_{q1}d\varsigma\in[-1,1]$.}\par
According to Lemma~\ref{lemma:1}, it is apparent that $\bm S_{r2}$ and $\bm S_{r1}$ have the subsequent relation:

@@

&\bm S_{r2}^T \bm{sign}(\bm S_{r2}) \ge  \bm S_{r1}^T \bm{sign}(\bm S_{r1})\\
&\bm{sign}(\bm S_{r2})=\bm{sign}(\bm S_{r1}),

@@

Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinates change $\bm S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $\bm S_{r2}$ holds results in the following expression:

@@

H(q)\dot {\bm S}_{r2} = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))-C(q,\dot q)\bm S_{r2}-Y_{r2}\Theta.

@@

V=\frac{1}{2}\bm S_{r2}^TH(q)\bm S_{r2}+\frac{1}{2}v^2,

@@

\dot V &= \bm S_{r2}^TH(q)\dot {\bm S}_{r2}+\frac{1}{2}\bm S_{r2}^T\dot H(q)\bm S_{r2}+v\dot v\\
&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TC(q,\dot q)\bm S_{r2}+\frac{1}{2}\bm S_{r2}^T\dot H(q)\bm S_{r2}-\bm S_{r2}^TY_{r2}\Theta+v\dot v\\
&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\Theta+\frac{1}{2}\bm S_{r2}^T(\dot H(q)-2C(q,\dot q))\bm S_{r2}+v\dot v\\
&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\Theta+v\dot v\\
&= -\bm S_{r2}^TR_M(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))\delta\varphi F(t) \bm{sign}(\bm S_{r1})+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{\bm r2}\Theta+v\dot v.\label{eq:V1_1}

@@

Since the command $ -\delta\varphi F(t) \bm S_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ such that $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain a diagonal matrix as follows:

@@

v\dot v =\varphi\delta \bm S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(\bm S_{r2}),

@@

utilizing $\bm{sign}(\bm S_{r1})=\bm{sign}(\bm S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:

@@

\dot V&\le -\bm S_{r2}^T\delta\varphi  K_1F(t)\bm{sign}(\bm S_{r2})+\bm S_{r2}^T(\varphi_1+\varphi_2) \bm{sign}(\bm S_{r2})+\varphi\delta \bm S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(\bm S_{r2})\\
&\le \varphi \bm S_{r2}^T\bm{sign}(\bm S_{r2})-\varphi\delta \bm S_{r2}^T \bm{sign}(\bm S_{r2})\\
&\le\varphi(1-\delta)\bm S_{r2}^T\bm{sign}(\bm S_{r2})\le 0

@@

where a large enough $\delta>1$ can be selected such that $\dot V \le 0$. According to the description of Barbalat¡¯s lemmas, it implies that $\bm S_{r2}$ asymptotically converges to origin. Also, the finite convergent time of desired sliding surface can be calculated by referring to~\cite{Ma201667}.}\par
\textcolor{red}{Utilizing $\bm S_{r2}=0$ leads to the equation

@@

\bm S_{q2}=-\bm{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma),\label{eq:eqSq2}

@@

and for employing Lyapunov second method to analyse the stabilities of $\bm S_{q2}$ and $\Delta\bm q$, we firstly select a Lyapunov function candidate

@@

V_1 = \frac{1}{2}\bm S_{q2}^T\bm S_{q_2},

@@

\dot V_1 &= \bm S_{q2}^T\dot {\bm S}_{q_2}\\
&=-\frac{\gamma \bm S_{q2}^TS_{q1}}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert^2}}\\
&\le -\frac{\gamma \Vert \bm S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert^2}}\le 0,

@@

if and only if $\bm S_{q1} = 0$, accordingly, $\bm S_{q2} = 0$, one has $\dot V_1=0$. Hence the asymptotically stability of Eq.~(\ref{eq:eqSq2}) has been proved, and therefore $\bm S_{q2}\rightarrow 0$ as $t\rightarrow \infty$ induces

@@

\dot Z = \vert Z\vert^{\hat\alpha} {sign}(Z),

@@

\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r3}))

@@

\bm S_{r3} &= \bm S_{q3}+\gamma\int^t_{t_0}\vert \bm S_{q3}(\varsigma)\vert^{\hat\alpha}  \bm{sign}(\bm S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
\bm S_{q3} &= \Delta \dot {\bm q}+\alpha \bm{Sine}(\xi\Delta \bm q),\label{eq:Sq3}

@@

where $0<\hat\alpha< 1$, such that the dynamics~(\ref{eq:dynamic model 2}) can be regulated as desired. $\bm y=\vert \bm x\vert^{\hat\alpha}$ is defined as $\vert \bm x\vert^{\hat\alpha} =\left(\vert x_1\vert^{\hat\alpha},\vert x_2\vert^{\hat\alpha},\cdots,\vert x_n\vert^{\hat\alpha}\right)^T$. $\varphi$ is the boundedness of the lumped uncertainty, and can be obtained by referring to Theorem~\ref{thm:1}.

@@

If the designer parameter $\hat\alpha = 1$, the quasi-saturated terminal sliding mode control degenerates into the quasi-saturated sliding mode control. Compared with the saturated sliding mode control, $\bm S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method. This is because the establishment of the equation $\dot {\bm S}_{q3} = \gamma\vert \bm S_{q3}\vert^{\hat\alpha} \bm{ sign}(\bm S_{q3})$.

@@

\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r4})),

@@

\bm S_{r4} &= \bm S_{q4}+\gamma\int^t_{t_0}\bm S_{q4}(\varsigma) d\varsigma\\
\bm S_{q4} &= \bm{Sine}(\Delta \dot {\bm q}+\alpha\xi\vert\Delta \bm q\vert^{\hat\alpha}\bm{sign}(\Delta \bm q)),\label{eq:Sr4}
